Rotations and Insecticide Resistance the story

### 2019-03-08 inst/documents/rotations_notes.Rmd
preparing shinyapps deployment with mortality switch

@@

fix error
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 1e-04 , rot_interval = 10 , eff = 0.95 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0.01 , logy = FALSE , no_r_below_start = FALSE , min_rwr_interval = 5 , threshold = 0.9 , mort_or_freq ='mort' )

~ rot_interval > 0
in insecticide_check()
Error in genotype_freq(rfreq) : 
  argument "rfreq" is missing, with no default

>>>>

8/3/19
eeek, found that there is a cran package called rotations, and this seems to be messing up deployment to shinyapps

@@

why in this scenario does it rotate insecticides even though it starts below mortality threshold
(to do with min_rwr threshold)
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 1e-04 , rot_interval = 0 , eff = 0.9 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.6 , migration = 0.01 , cost = 0.01 , logy = FALSE , no_r_below_start = FALSE , min_rwr_interval = 5 , threshold = 0.9 , mort_or_freq ='mort' )

~ fix plot error when coverage==1
